---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# glancedata

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/gbasulto/glancedata.svg?branch=master)](https://travis-ci.org/gbasulto/glancedata)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/gbasulto/glancedata?branch=master&svg=true)](https://ci.appveyor.com/project/gbasulto/glancedata)
[![Codecov test coverage](https://codecov.io/gh/gbasulto/glancedata/branch/master/graph/badge.svg)](https://codecov.io/gh/gbasulto/glancedata?branch=master)
<!-- badges: end -->

Whenever I start working on a dataset, I need to take a glance at the data to see how the data are or it the format is the one that I am  expecting. I found myself coding similar lines over and over again with each data set I put my hands on. I decided to put that lines together in an R package so I and others can use them. I called it **`glancedata`**.

There are already some cool R packages to summarize dataframes. The ones that I use more often are [`skimr`](https://github.com/ropensci/skimr) and [`GGally`](https://ggobi.github.io/ggally/). 


```{r, echo =FALSE}
suppressPackageStartupMessages(library("glancedata"))
```


## Installation

You can install the released version of glancedata from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("glancedata")
```

## Functions

These are the main functions in the package.

```{r, echo = FALSE, message=FALSE}

library(dplyr)

pkg_list <- list(

  ## glance_data
  c(
    fnct = "`glance_data`",
    des = "Alternative to `summary`. Emphasizes missing data and binary variables."
  ),
  
  ## glance_data_in_workbook
  c(
    fnct = "`glance_data_in_workbook`",
    des = "Similar to `glance_data`. Creates list of dataframes instead and saves XLSX file."
  ),
  
  ## plot_numerical_vars
  c(
    fnct = "`plot_numerical_vars`",
    des = "Creates a plot per numerical variable. It might be histogram, density plot, qqplot, violin plot or scatterplot."
  )
,
  
  ## plot_discrete_vars
  c(
    fnct = "`plot_discrete_vars`",
    des = "Creates a plot per numerical variable. It might be histogram, density plot, qqplot, violin plot or scatterplot."
  )
) ## End list


pkg_list %>%
  purrr::map_df(~ tibble(Function = .x[1], 
                         Description = .x[2])) %>%
  knitr::kable()
  
```




## Example

You can copy and paste the code and use your own dataset. I am using the `mtcars` dataframe.

```{r example, eval=FALSE}

library(glancedata)

## This will generate a dataframe
glance_data(mtcars)

## Create a list of dataframes. If you provide the `filename` 
## parameter to be equal to, say, "myglance.xlsx", then it will create
## an Excel workbook and place the content of each dataframe in a 
## separate sheet.
glance_data_in_workbook(mtcars)

## These are the types of plots for numerical variables
plot_numerical_vars(mtcars, plot_type = "density")
plot_numerical_vars(mtcars, plot_type = "pairwise")
plot_numerical_vars(mtcars, plot_type = "histogram")
plot_numerical_vars(mtcars, plot_type = "violin")
plot_numerical_vars(mtcars, plot_type = "boxplot")
plot_numerical_vars(mtcars, plot_type = "qqplot")

## ... And here are barplots for variables with only a few different 
## values
plot_discrete_vars(mtcars)
plot_discrete_vars(mtcars, sort_by_frequency = TRUE)

```

