---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# glancedata

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/gbasulto/glancedata.svg?branch=master)](https://travis-ci.org/gbasulto/glancedata)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/gbasulto/glancedata?branch=master&svg=true)](https://ci.appveyor.com/project/gbasulto/glancedata)
[![Codecov test coverage](https://codecov.io/gh/gbasulto/glancedata/branch/master/graph/badge.svg)](https://codecov.io/gh/gbasulto/glancedata?branch=master)
<!-- badges: end -->

Whenever I start working on a dataset, I need to take a glance at the data to see how the data are or it the format is the one that I am  expecting. I found myself coding similar lines over and over again with each data set I put my hands on. I decided to put that lines together in an R package so I and others can use them. I called it **`glancedata`**.

There are some already cool R packages to summarize information. Two of the best, in my opinion, are `skimr` and `GGally`. In this vignette, I provide examples of the functions in `glancedata` as well as some of the functions in these two packages.

## Installation

You can install the released version of glancedata from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("glancedata")
```

## Functions
Whenever I start working on a dataset, I need to take a glance at the data to see how the data are or it the format is the one that I am  expecting. I found myself coding similar lines over and over again with each data set I put my hands on. I decided to put that lines together in an R package so I and others can use them. I called it **`glancedata`**.

There are some already cool R packages to summarize information. Two of the best, in my opinion, are `skimr` and `GGally`. In this vignette, I provide examples of the functions in `glancedata` as well as some of the functions in these two packages.

Below is a table with the functions shown in this vignette.


```{r, echo = FALSE, message=FALSE}

library(dplyr)

pkg_list <- list(

  ## glance_data
  c(
    fnct = "`glance_data`",
    des = "Alternative to `summary`. Emphasizes missing data and binary variables."
  ),
  
  ## glance_data_in_workbook
  c(
    fnct = "`glance_data_in_workbook`",
    des = "Similar to `glance_data`. Creates list of dataframes instead and saves XLSX file."
  ),
  
  ## plot_numerical_vars
  c(
    fnct = "`plot_numerical_vars`",
    des = "Creates a plot per numerical variable. It might be histogram, density plot, qqplot, violin plot or scatterplot."
  )
,
  
  ## plot_discrete_vars
  c(
    fnct = "`plot_numerical_vars`",
    des = "Creates a plot per numerical variable. It might be histogram, density plot, qqplot, violin plot or scatterplot."
  )
) ## End list


pkg_list %>%
  purrr::map_df(~ tibble(Function = .x[1], 
                         Description = .x[2])) %>%
  knitr::kable()
  
```




## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(glancedata)
## basic example code
```

